Appendix 6: sdmTMB speed testing methods and model validation description

### 2022-01-28 doc/appendix-validation.Rmd
Change mgcv jitter

We can see the predictions match nearly exactly.
Furthermore, we can use the in-development function `sdmTMB::plot_smooth()` to compare the smoothers themselves.
Note that the sdmTMB version shows the marginal effect of a prediction including the intercept whereas the `mgcv::plot.gam()` shows the smooth component only.
We therefore use `mgcv::predict.gam()` to make a matching plot.
Below, we add a tiny jitter amount (`0.02`) to the mgcv output just so the two smoothers can both be visualized.
The blue lines are from mgcv and the black lines are from sdmTMB.

```{r plot-smooth, echo=TRUE, fig.asp=0.6, out.width="5in"}
plot_smooth(m)

x2 <- seq(0, 1, length.out = 100)
p_mgcv <- predict(m_mgcv, newdata = data.frame(x2 = x2), se.fit = TRUE)
qv <- stats::qnorm(1 - (1 - 0.95) / 2)
df <- data.frame(
  x2 = x2,
  est = p_mgcv$fit, 
  lwr = p_mgcv$fit - qv * p_mgcv$se.fit, 
  upr = p_mgcv$fit + qv * p_mgcv$se.fit
)
lines(df$x2, df$est + 0.02, col = "blue")
lines(df$x2, df$lwr + 0.02, lty = 2, col = "blue")
lines(df$x2, df$upr + 0.02, lty = 2, col = "blue")
```

>>>>

We can see the predictions match nearly exactly.
Furthermore, we can use the in-development function `sdmTMB::plot_smooth()` to compare the smoothers themselves.
Note that the sdmTMB version shows the marginal effect of a prediction including the intercept whereas the `mgcv::plot.gam()` shows the smooth component only.
We therefore use `mgcv::predict.gam()` to make a matching plot.
Below, we add a tiny jitter amount (`0.04`) to the mgcv output just so the two smoothers can both be visualized.
The blue lines are from mgcv and the black lines are from sdmTMB.

```{r plot-smooth, echo=TRUE, fig.asp=0.8, out.width="5in"}
par(cex = 0.8)
# sdmTMB:
plot_smooth(m)

# mgcv:
x2 <- seq(0, 1, length.out = 100)
p_mgcv <- predict(m_mgcv, newdata = data.frame(x2 = x2), se.fit = TRUE)
qv <- stats::qnorm(1 - (1 - 0.95) / 2)
df <- data.frame(
  x2 = x2,
  est = p_mgcv$fit, 
  lwr = p_mgcv$fit - qv * p_mgcv$se.fit, 
  upr = p_mgcv$fit + qv * p_mgcv$se.fit
)
lines(df$x2, df$est + 0.04, col = "blue")
lines(df$x2, df$lwr + 0.04, lty = 2, col = "blue")
lines(df$x2, df$upr + 0.04, lty = 2, col = "blue")
```
